\documentclass[11pt,a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath,amsfonts,amssymb}
\usepackage{graphicx}
\usepackage{hyperref}

\title{Your Paper Title Here}
\author{
    Author Name\\
    Department Name\\
    University/Institution Name\\
    Email Address
}
\date{\today} % Date, can be changed to a specific date

\begin{document}

\maketitle

\begin{abstract}
This is the abstract of your document. Here you briefly summarize the main points, findings, and conclusions of your paper. It should be concise and informative, providing an overview of the content that follows.
\end{abstract}

\section{Introduction}
Introduce the topic of your paper here. Explain the background, the problem you are addressing, and the main objectives of your paper.

\subsection{Subsection Title}
Detail specific aspects of the topic here. Subsections help organize the content into manageable parts.

\section{Literature Review}
Discuss relevant previous work by other authors in this section. A literature review typically surveys, summarizes, and analyzes published work on a topic.

\subsection{Subsection Title}
Break down different themes or aspects of the literature you are discussing.

\section{Methodology}
Describe the methods used in your research or analysis. This could include experimental methods, analytical models, or other approaches.

\subsection{Subsection Title}
Discuss specific parts of your methodology, such as data collection, experimental setup, etc.

\section{Results}
Present the findings of your research or analysis. Include data, observations, and any other relevant information.

\subsection{Subsection Title}
You might want to break down your results into different themes or categories.

\section{Discussion}
Interpret and discuss the significance of your results. Compare them with previous work, and discuss their implications.

\subsection{Subsection Title}
Discuss specific aspects of your results and their broader implications.

\section{Conclusion}
Summarize the main findings of your paper, their importance, and potential future work.

\section*{Acknowledgments}
Acknowledge anyone who helped you with your research, including funders, advisors, or others.

\begin{thebibliography}{9}
\bibitem{ref1}
Author Name, \textit{Paper Title}, Journal/Conference, Year.

% More bibliography items here
\end{thebibliography}

\end{document}
